Adopting agile in the large: motivations, success factors and challenges

### 2014-05-15 journal/article.tex
Editing

@@

\begin{table}[bh]
    \begin{tabular}{ l r }
        \toprule
        Business area    &  Case organizations   \\
        \midrule
		Online services for consumers and business  &  9  \\
		Telecommunications                          &  7  \\
		Enterprise management                       &  5  \\
		Banking and financial services              &  4  \\
		Healthcare                                  &  3  \\
		IT services                                 &  2  \\
		Government                                  &  1  \\
		Information security                        &  1  \\
		Not specified                               & 10  \\
        \midrule
		Total                                       & 42  \\
        \bottomrule
    \end{tabular}
    \caption{Business areas of case organizations in primary studies}
    \label{table:businessareas}
\end{table}

@@

@@

@@

Any organizational transformation involving numerous individuals will face some
challenges. As stated by Research Question 3, we investigated what are typical
challenges that large organizations introducing agile methods face.

@@

@@

To start a transformation the organization needs an initial push. However,
people are usually disinclined to change, and it any organizational change
should anticipate some resistance. People will not be willing to change unless
there are good reasons, and the change is preceived easy enough. It is difficult
to attain a buy-in for a change, and even organizations that have a flexible
culture will face resistance [P10]. It should be expected that not everyone will
be willing to change, and some employees will never adapt to the change [P6].
During a transformation period objections to change may become a major reason
for loss in time and productivity [P29].

On a team level numoerous reasons for change resistance were given. For
instance, Fecarotta [P14] described the organization of Boeing as risk-averse
and cautious which slows down any change. The organization was also described
having a deeply rooted status-quo because of high employee retention, which
further hindered change [P14]. In some cases it was reported that people worried
about new roles and responsibilities that agile would possibly bring [P44]. For
instance, testers were worried that they would need to take on cross functional
tasks, which would be outside their area of expertise [P18]. Yet another reason
for change resistance was the move from own offices to team areas [P22]. People
were also feeling being monitored because of the increased level of interaction
within the team and between project stakeholders [P45]. One study reported the
cultural change required for middle management as the biggest cause of
resistance [P2].

@@

The primary studies revealed challenges which relate particularly to large
scale. Additional layers of management are usually necessary to steer large
groups of people, but agile methods provide little guidance on how to organize
management. Also, as large organizations accomodate many development teams there
may be problems if the development models between teams are not synchronized.
Internal fragmenttation is a further problem that may be encountered in large
organizations.

@@

The existence of additional management positions may pose problems to agile
processes that emphasize self organization.
The role of middle management was seen as unclear in agile methods [P2]. This is
problematic as an agile transformation requires cultural change especially on
the middle management level [P2].
It was described that people in management positions needed to resist the
tendency to take command and control to allow room for self organization, but
the change in role was difficult to achieve for the people involved [P11, P52].
Nielsen and McMunn [P30] describe how the project management group had
previously worked through big up front plans and competing of resources, but
those ways would need to dramatically change.

@@

In most cases a large organizational transformation proceeded gradually, and
during the process it was possible that the new agile model was used in parallel
with the old methods. The arrangement of using the old and new models side by
side was seen as problematic [P1, P26], and causing tensions on all
organizational levels [P10]. Ongoing projects had been set up with previous
development methods, and the agile methods needed to be arranged to fit with
them [P8, P29]. A particular problem in collaborating between projects using
different models was that in Scrum the software design was fleshed out over time
as sprints progressed, but the waterfall model would require detailed design to
be locked early in the project [P29].

Despite the agile introduction there were problems with management working
according to the old waterfall model. O'Connor [P38] described management as
``focused on meetings and big up front project plans'' despite agile being in
use. In another case management was losing confidence in agile because familiar
reports on cost analysis and percentage complete were not produced [P35]. As
Scrum teams did not commit to fixed schedules they were considered unreliable
according to the original model [P45].

@@

In addition to teams using agile and waterfall methods side by side it is
possible in a large organization that the agile interpretations of teams start
diverging. When many teams implement agile without consistent guidance friction
and fragmentation may be generated [P9]. The organization may require moving
people between teams from time to time, and therefore it would be desirable that
no big differences in teams' agile cultures exist. Divergence in process would
create risk increasing costs when relocating people [P38].
Further, if processes of teams diverged management had difficulties in
forecasting and comparing work of different teams [P38, P48]. To overcome
problems with divergence in agile models some organizations defined standards to
follow [P8, P43].

>>>>

* Scrum master must not command and control -- Scrum master as manager??

@@

@@

\begin{table}[!t]
    \begin{tabular}{ l r }
        \toprule
        Business area    &  Case organizations   \\
        \midrule
		Online services for consumers and business  &  9  \\
		Telecommunications                          &  7  \\
		Enterprise management                       &  5  \\
		Banking and financial services              &  4  \\
		Healthcare                                  &  3  \\
		IT services                                 &  2  \\
		Government                                  &  1  \\
		Information security                        &  1  \\
		Not specified                               & 10  \\
        \midrule
		Total                                       & 42  \\
        \bottomrule
    \end{tabular}
    \caption{Business areas of case organizations in primary studies}
    \label{table:businessareas}
\end{table}

@@

\clearpage

@@

Any organizational transformation involving numerous individuals will face some
challenges. As stated by Research Question 3, we investigated what challenges
large organizations introducing agile methods may face.

@@

\begin{figure}[!b]
  \begin{center}
    \includegraphics{graphics/challenges_summary.pdf}
    \caption{Challenges in agile transformation}
    \label{fig:challenges_summary}
  \end{center}
\end{figure}

@@

In an organizational transformation working habits and roles need to change.
However, people are usually disinclined to change and some resistance should be
anticipated in any change process. People will not be willing to change unless
there are good reasons, and the change is preceived easy enough. It is difficult
to attain a buy-in for a change, and even organizations that have a flexible
culture will face resistance [P10]. It should be expected that not everyone will
be willing to change, and some employees will never adapt to the change [P6].
During a transformation period objections to change may become a major reason
for loss in time and productivity [P29].

On a team level numoerous reasons for change resistance were given. For
instance, Fecarotta [P14] described the organization of Boeing as risk-averse
and cautious which slows down any change. The organization was also described
having a deeply rooted status-quo because of high employee retention, which
further hindered change [P14]. In some cases it was reported that people worried
about new roles and responsibilities that the agile model might bring [P44]. For
instance, testers were worried that they would need to take on cross functional
tasks, which would be outside their area of expertise [P18]. Yet another reason
for change resistance was the move from own offices to team areas [P22]. People
were also feeling being monitored because of the increased level of interaction
within the team and between project stakeholders [P45]. One study reported the
cultural change required for middle management as the biggest cause of
resistance [P2].

@@

The primary studies revealed challenges that relate particularly to large
scale. Additional layers of management are usually necessary to steer large
groups of people, but agile methods provide little guidance on how to organize
management. Problems may arise in a large environment if the schedule of agile
adoption varies from team to team. Internal fragmenttation is a further problem
that may be encountered in large organizations.

@@

The existence of additional management positions may pose problems to agile
processes that emphasize self organization.
Especially the role of middle management was seen as unclear in agile methods
[P2]. This is problematic as an agile transformation requires cultural change
particularly on the middle management level [P2].
It was described that managers needed to resist the tendency to take command and
control and allow room for self organization, but the change in role was
difficult to achieve for the people involved [P11, P52].
Nielsen and McMunn [P30] describe how the project management group had
previously worked through big up front plans and competing of resources, but
those ways would need to dramatically change.

@@

In most cases a large organizational transformation proceeded gradually, and
during the process it was possible that the new agile model was used in parallel
with the old methods. The arrangement of using the old and new models side by
side was seen as generally problematic [P1, P26], and causing tensions on all
organizational levels [P10]. Ongoing projects had been set up with previous
development methods, and the agile methods needed to be arranged to fit along
with them [P8, P29]. A particular problem in collaborating between projects
using different models was that in Scrum the software design was fleshed out
over time as sprints progressed, but the waterfall model would require detailed
design to be locked early in the project [P29].

Even when agile had been taken into use in development there were problems with
management working according to the old waterfall model. O'Connor [P38]
described management as ``focused on meetings and big up front project plans''
despite agile being in use. In another case management was losing confidence in
agile because familiar reports on cost analysis and percentage complete were not
produced [P35]. As Scrum teams did not commit to fixed schedules they were
considered unreliable according to the original model [P45].

@@

In addition to teams using agile and waterfall models side by side a large
organization makes it possible that the agile interpretations of teams diverge.
When many teams implement agile without consistent guidance friction and
fragmentation may emerge [P9]. The organization may require moving people
between teams from time to time, and therefore it would be desirable that no big
differences in teams' agile cultures exist. Divergence in process would create
risk of increased costs when relocating people [P38].
Further, if processes of teams diverged management had difficulties in
forecasting and comparing work of different teams [P38, P48]. To overcome
problems with divergence in agile models some organizations defined standards to
follow [P8, P43].
